---
title: "shinytdmore introduction"
author: "Ruben Faelens"
date: "09/07/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shinytdmore introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, echo=FALSE}
library(shinytest)

tmp_lib <- tdmore::ensurePackagePresent("shinytdmore", quiet=F)
app <- withr::with_libpaths(tmp_lib, {
      ShinyDriver$new(path="shinytdmoreApp", debug="all", shinyOptions = list(test.mode=TRUE))
    }, action="prefix")

file <- knitr::fig_path("png")
dir.create(dirname(file), recursive = TRUE, showWarnings = FALSE) #create dir if not exists yet

knitr::opts_chunk$set(echo=FALSE)
```

## Introduction
Shinytdmore helps you build an application for dose adaptation. This vignette will take you through the application step-by-step.

## Prediction tab default menu
```{r}
Sys.sleep(2)
file <- knitr::fig_path("png")
app$takeScreenshot(file)
knitr::include_graphics(file)
```


## Add the posology
```{r}
app$setInputs(`prediction-doses-add`="click")
app$setInputs(`prediction-doses-add`="click")
app$setInputs(`prediction-doses-add`="click")

Sys.sleep(2)
app$findElement(".htCheckboxRendererInput")$click() #FIX the first dose
Sys.sleep(2)

file <- knitr::fig_path("png")
app$takeScreenshot(file)
knitr::include_graphics(file)
```
When you add a dose, the default formulation in the model is used. Clicking *add dose* multiple times will add new doses with the right interdose interval.

## Add an observation
```{r}
app$setInputs(`prediction-observation-add`="click")
table <- app$findElements("#prediction-observation-table-table td")
table[[2]]$click()
table[[2]]$sendKeys("06:50\t")
table[[3]]$click()
table[[3]]$sendKeys("43.5\t")

Sys.sleep(2)
file <- knitr::fig_path("png")
app$takeScreenshot(file)
knitr::include_graphics(file)
```

The observation is not used yet, because the current time ("now") is still 1st of January at midnight.

## Changing the now time
```{r}
now <- app$findElement("#prediction-now-now")
now$click()

combodate <- app$findElements(".popover-content .combodate select")
combodate[[4]]$setValue("11")

submit <- app$findElement(".popover-content .editable-submit")
submit$click()

file <- knitr::fig_path("png")
app$takeScreenshot(file)
knitr::include_graphics(file)
```

The observation is now taken into account. From the population plot, we see that this individual has relatively low concentrations with regards to the starting dose.

## Prediction graph
```{r}
app$findElement(linkText="Fit")$click()
#app$getDebugLog()
Sys.sleep(5)
file <- knitr::fig_path("png")
app$takeScreenshot(file)
knitr::include_graphics(file)
```

## Recommendation
```{r}
app$findElement(linkText="Recommendation")$click()
#app$getDebugLog()
Sys.sleep(5)
file <- knitr::fig_path("png")
app$takeScreenshot(file)
knitr::include_graphics(file)
```


## Final debug log
```{r}
app$getDebugLog()
app$stop()
```